Canonical rings of $\bq$-divisors on Minimal Rational Surfaces

### 2015-07-17 surfaces-write-up/surface-write-up.tex

\section{Canonical Rings on Hirzebruch surfaces}
\label{sec:hirz}

In this section, the main aim is to prove Theorem ~\ref{thm:}, bounding the degree of generators and relations of the canonical ring of a $\bq$-divisor on any Hirzebruch surface.

>>>>

\section{Canonical Rings on Hirzebruch surfaces}
\label{sec:hirz}
In this section, the main aim is to prove Theorem
~\ref{thm:hirz-generators-relations}, bounding the degree of
generators and relations of the canonical ring of a $\bq$-divisor
on any Hirzebruch surface.
